Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-04-02 Documents/M1/realizableFermionicM1/sections/appendix.tex
Added the details of IMEX RKCB2.
Added the details of IMEX SSP2332.

@@

>>>>

A second-order accurate, diffusion accurate, L-stable, strong-stability-preserving IMEX scheme was given in \cite{cavaglieriBewley2015}.  
We refer to this scheme as IMEX RKCB2.  
Its non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 2/5, \nonumber \\
  \tilde{a}_{32} &= 1, \nonumber \\
  a_{22} &= 2/5, \nonumber \\
  a_{32} &= 5/6, \quad a_{33} = 1/6. \nonumber
\end{align}
And $w_{i} = a_{3i} = \tilde{w}_{i}$ for stiff accuracy.
CFL ...

@@

A second-order accurate, diffusion accurate, L-stable, strong-stability-preserving IMEX scheme was given in \cite{pareschiRusso_2005}.  
We refer to this scheme as IMEX SSP2332.  
Its non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 1/2, \nonumber \\
  \tilde{a}_{31} &= 1/2, \quad \tilde{a}_{32} = 1/2, \nonumber \\
  a_{11} &= 1/4, \nonumber \\
  a_{22} &= 1/4, \nonumber \\
  a_{31} &= 1/3, \quad a_{32} = 1/3, \quad a_{33} = 1/3. \nonumber
\end{align}
And $w_{i} = a_{3i} = \tilde{w}_{i}$ for stiff accuracy.
CFL ...
